---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```
```{r}
results <- read.csv("Listening Test FInal_April 6, 2022_01.28.csv")
```

```{r}
results_cut_down <- subset(results, select=c(StartDate, EndDate, Progress, Duration..in.seconds.,                                  Finished, RecordedDate, DistributionChannel, Q1, Q2, Q3, 17:99))

results_cut_down <- results_cut_down[results_cut_down$DistributionChannel %in% c("anonymous"), ]

results_cut_down <- results_cut_down %>%
                        select(-c(Q6_1, Q8_1))
                      

# cut any rows with $DistributionChannel == Preview
```

# to do: do a boxplot of the answers to each question, and a big boxplot of the combined numbers for each voice variant

# Sentence 1 (Question 4): just to get started:

```{r}
results_S1_long <- results_cut_down %>%
               select(c(Q4_1:Q4_8)) %>%
               pivot_longer(Q4_1:Q4_8, names_to="version_number", values_to="result")
results_S1_long$result <- as.numeric(results_S1_long$result)              
```


```{r}
ggplot(data=results_S1_long, aes(x = version_number, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("Sentence 1") +
theme(plot.title = element_text(hjust = 0.45))
```
TO DO: NOW MARK WHAT VOICE EACH SENTENCE IS FROM ON THE INDIVIDUAL DATAFRAME, THEN STICK ALL OF THE 
INDIVIDUAL SENTENCE DATAFRAMES TOGETHER AND BOXPLOT THE SCORES FOR EACH 

3, 2, 4, 1, 6, 5, 7, 8

1. Arctic_a_voice_build original 
2. Arctic _a reduced_mixture models 
3. Arctic_a reduced training sentences 
4. SPT_initial_voice_build 
5. SPT_reduced_mixture_models 
6. SPT_reduced training sentences 
7. Hybrid Voice 
8. reference

```{r}
sentence_1_order = c(3, 2, 4, 1, 6, 5, 7, 8)

results_S1_long <-
results_S1_long %>%
                  mutate(voice_num = 
                           ifelse(version_number=="Q4_1", 3,
                           ifelse(version_number=="Q4_2", 2,
                           ifelse(version_number=="Q4_3", 4,
                           ifelse(version_number=="Q4_4", 1,
                           ifelse(version_number=="Q4_5", 6,
                           ifelse(version_number=="Q4_6", 5,
                           ifelse(version_number=="Q4_7", 7,
                                  8))))))))

results_S1_long$voice_num <- as.character(results_S1_long$voice_num)
```

# new boxplot of S1 data but with voice num:

```{r}
ggplot(data=results_S1_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("Sentence 1") +
theme(plot.title = element_text(hjust = 0.45))
```
TO DO: NOW DO A 'LONG' DF FOR EACH OF QUESTIONS 3,  LIKE ABOVE FOR S1, AND THEN STICK S1, S3, S4 and S5 DF'S TOGETHER (all for SPT test sentences except question 2 which is for sub-cost test) AND PLOT AGAIN

S3 DONE
S4 DONE
S5 DONE

#S3
```{r}
results_S3_long <- results_cut_down %>%
               select(c(Q6_2:Q6_8)) %>%
               pivot_longer(Q6_2:Q6_8, names_to="version_number", values_to="result")
results_S3_long$result <- as.numeric(results_S3_long$result) 

sentence_3_order = c(4, 8, 7, 3, 2, 5, 1, 6)

results_S3_long <-
results_S3_long %>%
                  mutate(voice_num = 
                           ifelse(version_number=="Q6_1", 4,
                           ifelse(version_number=="Q6_2", 8,
                           ifelse(version_number=="Q6_3", 7,
                           ifelse(version_number=="Q6_4", 3,
                           ifelse(version_number=="Q6_5", 2,
                           ifelse(version_number=="Q6_6", 5,
                           ifelse(version_number=="Q6_7", 1,
                                  6))))))))

results_S3_long$voice_num <- as.character(results_S3_long$voice_num)
```

```{r}
ggplot(data=results_S3_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("Sentence 3") +
theme(plot.title = element_text(hjust = 0.45))
```
#S4
```{r}
results_S4_long <- results_cut_down %>%
               select(c(Q7_1:Q7_8)) %>%
               pivot_longer(Q7_1:Q7_8, names_to="version_number", values_to="result")
results_S4_long$result <- as.numeric(results_S4_long$result) 

sentence_4_order = c(3, 7, 4, 2, 1, 6, 8, 5)

results_S4_long <-
results_S4_long %>%
                  mutate(voice_num = 
                           ifelse(version_number=="Q7_1", 3,
                           ifelse(version_number=="Q7_2", 7,
                           ifelse(version_number=="Q7_3", 4,
                           ifelse(version_number=="Q7_4", 2,
                           ifelse(version_number=="Q7_5", 1,
                           ifelse(version_number=="Q7_6", 6,
                           ifelse(version_number=="Q7_7", 8,
                                  5))))))))

results_S4_long$voice_num <- as.character(results_S4_long$voice_num)
```

```{r}
ggplot(data=results_S4_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("Sentence 4") +
theme(plot.title = element_text(hjust = 0.45))
```
#S5
```{r}
results_S5_long <- results_cut_down %>%
               select(c(Q8_2:Q8_8)) %>%
               pivot_longer(Q8_2:Q8_8, names_to="version_number", values_to="result")
results_S5_long$result <- as.numeric(results_S5_long$result) 

sentence_5_order = c(4, 3, 2, 6, 8, 7, 5, 1)

results_S5_long <-
results_S5_long %>%
                  mutate(voice_num = 
                           ifelse(version_number=="Q8_1", 4,
                           ifelse(version_number=="Q8_2", 3,
                           ifelse(version_number=="Q8_3", 2,
                           ifelse(version_number=="Q8_4", 6,
                           ifelse(version_number=="Q8_5", 8,
                           ifelse(version_number=="Q8_6", 7,
                           ifelse(version_number=="Q8_7", 5,
                                  1))))))))

results_S5_long$voice_num <- as.character(results_S5_long$voice_num)
```

```{r}
ggplot(data=results_S5_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("Sentence 5") +
theme(plot.title = element_text(hjust = 0.45))
```
```{r}
results_spt_sentences_long <- rbind(results_S1_long, results_S3_long, results_S4_long, results_S5_long)
```

```{r}
# do a version_name column, which will be universal based on ifelse of the voice_num column (i.e. this
# shouldn't need to be changed for each question)
results_spt_sentences_long <-
results_spt_sentences_long %>%
                  mutate(voice_name= 
                           ifelse(voice_num=="1", "Arctic A Original",
                           ifelse(voice_num=="2", "Arctic A Reduced Mixture Models",
                           ifelse(voice_num=="3", "Arctic A Reduced Training Sentences",
                           ifelse(voice_num=="4", "SPT Original",
                           ifelse(voice_num=="5", "SPT Reduced Mixture Models",
                           ifelse(voice_num=="6", "SPT Reduced Training Sentences",
                           ifelse(voice_num=="7", "Hybrid Voice",
                                  "Reference"))))))))


```

```{r}
spt_plot <- ggplot(data=results_spt_sentences_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("SPT Sentences Results") +
theme(plot.title = element_text(hjust = 0.45))
spt_plot
```
# TO DO: CREATE LONG DF'S AND STICK TOGETHER FOR 

S6 DONE
S7 DONE
S8 DONE
S9 DONE
S10 DONE

#S6
```{r}
results_S6_long <- results_cut_down %>%
               select(c(Q9_1:Q9_8)) %>%
               pivot_longer(Q9_1:Q9_8, names_to="version_number", values_to="result")
results_S6_long$result <- as.numeric(results_S6_long$result) 

sentence_6_order = c(5, 2, 8, 4, 6, 3, 1, 7)

results_S6_long <-
results_S6_long %>%
                  mutate(voice_num = 
                           ifelse(version_number=="Q9_1", 5,
                           ifelse(version_number=="Q9_2", 2,
                           ifelse(version_number=="Q9_3", 8,
                           ifelse(version_number=="Q9_4", 4,
                           ifelse(version_number=="Q9_5", 6,
                           ifelse(version_number=="Q9_6", 3,
                           ifelse(version_number=="Q9_7", 1,
                                  7))))))))

results_S6_long$voice_num <- as.character(results_S6_long$voice_num)
```

```{r}
ggplot(data=results_S6_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("Sentence 6") +
theme(plot.title = element_text(hjust = 0.45))
```
#S7
```{r}
results_S7_long <- results_cut_down %>%
               select(c(Q10_1:Q10_8)) %>%
               pivot_longer(Q10_1:Q10_8, names_to="version_number", values_to="result")
results_S7_long$result <- as.numeric(results_S7_long$result) 

sentence_7_order = c(4, 7, 1, 8, 6, 3, 2, 5)

results_S7_long <-
results_S7_long %>%
                  mutate(voice_num = 
                           ifelse(version_number=="Q10_1", 4,
                           ifelse(version_number=="Q10_2", 7,
                           ifelse(version_number=="Q10_3", 1,
                           ifelse(version_number=="Q10_4", 8,
                           ifelse(version_number=="Q10_5", 6,
                           ifelse(version_number=="Q10_6", 3,
                           ifelse(version_number=="Q10_7", 2,
                                  5))))))))

results_S7_long$voice_num <- as.character(results_S7_long$voice_num)
```

```{r}
ggplot(data=results_S7_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("Sentence 7") +
theme(plot.title = element_text(hjust = 0.45))
```

#S8
```{r}
results_S8_long <- results_cut_down %>%
               select(c(Q11_1:Q11_8)) %>%
               pivot_longer(Q11_1:Q11_8, names_to="version_number", values_to="result")
results_S8_long$result <- as.numeric(results_S8_long$result) 

sentence_8_order = c(2, 3, 8, 5, 1, 7, 6, 4)

results_S8_long <-
results_S8_long %>%
                  mutate(voice_num = 
                           ifelse(version_number=="Q11_1", 2,
                           ifelse(version_number=="Q11_2", 3,
                           ifelse(version_number=="Q11_3", 8,
                           ifelse(version_number=="Q11_4", 5,
                           ifelse(version_number=="Q11_5", 1,
                           ifelse(version_number=="Q11_6", 7,
                           ifelse(version_number=="Q11_7", 6,
                                  4))))))))

results_S8_long$voice_num <- as.character(results_S8_long$voice_num)
```

```{r}
ggplot(data=results_S8_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("Sentence 8") +
theme(plot.title = element_text(hjust = 0.45))
```

#S9
```{r}
results_S9_long <- results_cut_down %>%
               select(c(Q12_1:Q12_8)) %>%
               pivot_longer(Q12_1:Q12_8, names_to="version_number", values_to="result")
results_S9_long$result <- as.numeric(results_S9_long$result) 

sentence_9_order = c(1, 5, 6, 2, 3, 7, 4, 8)

results_S9_long <-
results_S9_long %>%
                  mutate(voice_num = 
                           ifelse(version_number=="Q12_1", 1,
                           ifelse(version_number=="Q12_2", 5,
                           ifelse(version_number=="Q12_3", 6,
                           ifelse(version_number=="Q12_4", 2,
                           ifelse(version_number=="Q12_5", 3,
                           ifelse(version_number=="Q12_6", 7,
                           ifelse(version_number=="Q12_7", 4,
                                  8))))))))

results_S9_long$voice_num <- as.character(results_S9_long$voice_num)
```

```{r}
ggplot(data=results_S9_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("Sentence 9") +
theme(plot.title = element_text(hjust = 0.45))
```

#S10

```{r}
results_S10_long <- results_cut_down %>%
               select(c(Q13_1:Q13_8)) %>%
               pivot_longer(Q13_1:Q13_8, names_to="version_number", values_to="result")
results_S10_long$result <- as.numeric(results_S10_long$result) 

sentence_10_order = c(8, 5, 3, 1, 7, 2, 4, 6)

results_S10_long <-
results_S10_long %>%
                  mutate(voice_num = 
                           ifelse(version_number=="Q13_1", 8,
                           ifelse(version_number=="Q13_2", 5,
                           ifelse(version_number=="Q13_3", 3,
                           ifelse(version_number=="Q13_4", 1,
                           ifelse(version_number=="Q13_5", 7,
                           ifelse(version_number=="Q13_6", 2,
                           ifelse(version_number=="Q13_7", 4,
                                  6))))))))

results_S10_long$voice_num <- as.character(results_S10_long$voice_num)
```

```{r}
ggplot(data=results_S10_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("Sentence 10") +
theme(plot.title = element_text(hjust = 0.45))
```
```{r}
results_arctic_b_sentences_long <- rbind(results_S6_long, results_S7_long, results_S8_long, results_S9_long, results_S10_long)
```

```{r}
results_arctic_b_sentences_long <-
results_arctic_b_sentences_long %>%
                  mutate(voice_name= 
                           ifelse(voice_num=="1", "Arctic A Original",
                           ifelse(voice_num=="2", "Arctic A Reduced Mixture Models",
                           ifelse(voice_num=="3", "Arctic A Reduced Training Sentences",
                           ifelse(voice_num=="4", "SPT Original",
                           ifelse(voice_num=="5", "SPT Reduced Mixture Models",
                           ifelse(voice_num=="6", "SPT Reduced Training Sentences",
                           ifelse(voice_num=="7", "Hybrid Voice",
                                  "Reference"))))))))
```

```{r}
ARCTIC_B_PLOT <- ggplot(data=results_arctic_b_sentences_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("ARCTIC B Sentences Results") +
theme(plot.title = element_text(hjust = 0.45))
```

```{r}
spt_plot

ARCTIC_B_PLOT
```

TO DO: THEN RUN T-TESTS FOR THE HYPOTHESES BASED ON THE BIG DF's for each test sentence group


HYPOTHESIS 1:

# SPT test sentence t-test

```{r}
results_spt_sentences_long_just_sentence_1_and_4 <- results_spt_sentences_long %>%
                                                   filter(voice_num == "1" | voice_num == "4")

```

```{r}
SPT_sentence_t_test <- with(results_spt_sentences_long_just_sentence_1_and_4, t.test(result ~ voice_num, alternative = "less"))
SPT_sentence_t_test
```
Boxplot to go with SPT test sentence t-test:


```{r}
SPT_1_AND_4_PLOT <- ggplot(data=results_spt_sentences_long_just_sentence_1_and_4, aes(x = voice_name, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("SPT test sentence original builds: ARCTIC A vs SPT Database Results") +
theme(plot.title = element_text(hjust = 0.45)) +
ylab("Score") +
xlab("Voice Name")
ggsave("SPT_1_AND_4_PLOT.png")

SPT_1_AND_4_PLOT 
```
```{r}
results_spt_sentences_long_just_voice_1 <- results_spt_sentences_long %>%
                                                   filter(voice_num == "1") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(results_spt_sentences_long_just_voice_1$result)         
mean(results_spt_sentences_long_just_voice_1$`result 1-5`)
sd(results_spt_sentences_long_just_voice_1$`result 1-5`)
```
```{r}
N = nrow(results_spt_sentences_long_just_voice_1)
C_I_95 = (1.96 * sd(results_spt_sentences_long_just_voice_1$`result 1-5`)) / sqrt(N)
C_I_95
```




```{r}
results_spt_sentences_long_just_voice_7 <- results_spt_sentences_long %>%
                                                   filter(voice_num == "7") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(results_spt_sentences_long_just_voice_7$result)         
mean(results_spt_sentences_long_just_voice_7$`result 1-5`)
sd(results_spt_sentences_long_just_voice_7$`result 1-5`)
```
```{r}
N = nrow(results_spt_sentences_long_just_voice_7)
C_I_95 = (1.96 * sd(results_spt_sentences_long_just_voice_7$`result 1-5`)) / sqrt(N)
C_I_95
```











```{r}
results_spt_sentences_long_just_voice_4 <- results_spt_sentences_long %>%
                                                   filter(voice_num == "4") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(results_spt_sentences_long_just_voice_4$result)         
mean(results_spt_sentences_long_just_voice_4$`result 1-5`)
sd(results_spt_sentences_long_just_voice_4$`result 1-5`)
```
```{r}
N = nrow(results_spt_sentences_long_just_voice_4)
C_I_95 = (1.96 * sd(results_spt_sentences_long_just_voice_4$`result 1-5`)) / sqrt(N)
C_I_95
```




# Arctic B test sentence t-test

```{r}
results_ARCTIC_B_sentences_long_just_sentence_1_and_4 <- results_arctic_b_sentences_long %>%
                                                   filter(voice_num == "1" | voice_num == "4")
```

```{r}
ARCTIC_B_sentence_t_test <- with(results_ARCTIC_B_sentences_long_just_sentence_1_and_4, t.test(result ~ voice_num, alternative = "greater"))
ARCTIC_B_sentence_t_test
```
Boxplot to go with SPT test sentence t-test:


```{r}
ARCTIC_1_AND_4_PLOT <- ggplot(data=results_ARCTIC_B_sentences_long_just_sentence_1_and_4, aes(x = voice_name, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("ARCTIC B test sentence original builds: ARCTIC A vs SPT Database Results") +
theme(plot.title = element_text(hjust = 0.45)) +
ylab("Score") +
xlab("Voice Name")
ggsave("ARCTIC_1_AND_4_PLOT.png")

ARCTIC_1_AND_4_PLOT 
```
```{r}
results_arctic_sentences_long_just_voice_4 <-  results_arctic_b_sentences_long %>%
                                                   filter(voice_num == "4") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(results_arctic_sentences_long_just_voice_4$result)         
mean(results_arctic_sentences_long_just_voice_4$`result 1-5`)
sd(results_arctic_sentences_long_just_voice_4$`result 1-5`)
```
```{r}
N = nrow(results_arctic_sentences_long_just_voice_4)
C_I_95 = (1.96 * sd(results_arctic_sentences_long_just_voice_4$`result 1-5`)) / sqrt(N)
C_I_95
```
```{r}
results_arctic_sentences_long_just_voice_7 <- results_arctic_b_sentences_long %>%
                                                   filter(voice_num == "7") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(results_arctic_sentences_long_just_voice_7$result)         
mean(results_arctic_sentences_long_just_voice_7$`result 1-5`)
sd(results_arctic_sentences_long_just_voice_7$`result 1-5`)
N = nrow(results_arctic_sentences_long_just_voice_7)
C_I_95 = (1.96 * sd(results_arctic_sentences_long_just_voice_7$`result 1-5`)) / sqrt(N)
C_I_95
```
```{r}
results_arctic_sentences_long_just_voice_1 <-  results_arctic_b_sentences_long %>%
                                                   filter(voice_num == "1") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(results_arctic_sentences_long_just_voice_1$result)         
mean(results_arctic_sentences_long_just_voice_1$`result 1-5`)
sd(results_arctic_sentences_long_just_voice_1$`result 1-5`)
```
```{r}
N = nrow(results_arctic_sentences_long_just_voice_1)
C_I_95 = (1.96 * sd(results_arctic_sentences_long_just_voice_1$`result 1-5`)) / sqrt(N)
C_I_95
```







# FOR REPORT: the difference in means in pretty consistent in both directions: i.e. when tested on SPT sentences, the SPT trained voice has a mean of about 50, whilst the ARCTIC voice has a mean of about 39, a statisically significant difference (p ~ 0.008). When tested on ARCTIC sentences, the ARCTIC trained voice has a mean of about 50, and the SPT voice has a mean of about 36, a statistically significant difference (p ~ 0.001)  


# Add a 'same_domain' boolean column to each of the longdf's

# SPT
```{r}
results_spt_sentences_long <- results_spt_sentences_long %>%
                                            filter(voice_num!= "7" & voice_num != "8")
                                    
results_spt_sentences_long <- results_spt_sentences_long %>%
                                       mutate(same_domain = 
                                                ifelse(voice_num %in% c(4, 5, 6), TRUE, FALSE))
```

# ARCTIC_B
```{r}
results_arctic_b_sentences_long <- results_arctic_b_sentences_long %>%
                                            filter(voice_num!= "7" & voice_num != "8")
                                    
results_arctic_b_sentences_long <- results_arctic_b_sentences_long %>%
                                       mutate(same_domain = 
                                                ifelse(voice_num %in% c(1, 2, 3), TRUE, FALSE))
```

# combine the two test_sentence longdf's into one df: DONE

```{r}
combined_long_df_arctic_b_and_spt <- rbind(results_spt_sentences_long, results_arctic_b_sentences_long)
```

TO DO: do a linear model

```{r}
same_domain_lm <- lm(result ~ same_domain, data = combined_long_df_arctic_b_and_spt)
summary(same_domain_lm)
```
```{r}
results_spt_sentences_long <- results_spt_sentences_long %>%
                                            filter(voice_num != "8")
                                    
results_spt_sentences_long <- results_spt_sentences_long %>%
                                       mutate(domain_1_2_3 = 
                                                ifelse(voice_num %in% c(4, 5, 6), "1", 
                                                ifelse(voice_num == 7, "2",
                                                       "3")))


results_arctic_b_sentences_long <- results_arctic_b_sentences_long %>%
                                          filter(voice_num != "8")
                                    
results_arctic_b_sentences_long <- results_arctic_b_sentences_long %>%
                                      mutate(domain_1_2_3 = 
                                               ifelse(voice_num %in% c(1, 2, 3), "1", 
                                                      ifelse(voice_num == 7, "2",
                                                      "3")))

combined_long_df_arctic_b_and_spt <- rbind(results_spt_sentences_long, results_arctic_b_sentences_long)

```

```{r}
domain_1_2_3_lm <- lm(result ~ domain_1_2_3, data = combined_long_df_arctic_b_and_spt)
summary(domain_1_2_3_lm)
```








```{r}

combined_long_df_arctic_b_and_spt <-  combined_long_df_arctic_b_and_spt %>%
                                                   mutate(result_1_5 = result/20)

same_domain_lm <- lm(result_1_5 ~ same_domain, data = combined_long_df_arctic_b_and_spt )
summary(same_domain_lm)
```






# HYPOTHESIS 2 TESTING

so test each test sentence set:


ARCTIC A > ARCTIC B: 

Voice 1 (Full) vs Voice 2 (reduced mixture models) 

On ARCTIC B sentences: 6, 7, 8, 9, 10


```{r}
hyp_2_arctic_results <- results_arctic_b_sentences_long %>%
                                     filter(voice_num == "1" | voice_num == "2")
```


```{r}
hyp_2_arctic_t_test <- with(hyp_2_arctic_results, t.test(result ~ voice_num, alternative = "greater"))
hyp_2_arctic_t_test
```
```{r}
results_arctic_sentences_long_just_voice_2 <-  results_arctic_b_sentences_long %>%
                                                   filter(voice_num == "2") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(results_arctic_sentences_long_just_voice_2$result)         
mean(results_arctic_sentences_long_just_voice_2$`result 1-5`)
sd(results_arctic_sentences_long_just_voice_2$`result 1-5`)
```
```{r}
N = nrow(results_arctic_sentences_long_just_voice_2)
C_I_95 = (1.96 * sd(results_arctic_sentences_long_just_voice_2$`result 1-5`)) / sqrt(N)
C_I_95
```





```{r}
hyp_2_spt_results <- results_spt_sentences_long %>%
                                     filter(voice_num == "4" | voice_num == "5")
```


```{r}
hyp_2_spt_t_test <- with(hyp_2_spt_results, t.test(result ~ voice_num, alternative = "greater"))
hyp_2_spt_t_test
```
```{r}
results_spt_sentences_long_just_voice_5 <-  hyp_2_spt_results %>%
                                                   filter(voice_num == "5") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(results_spt_sentences_long_just_voice_5$result)         
mean(results_spt_sentences_long_just_voice_5$`result 1-5`)
sd(results_spt_sentences_long_just_voice_5$`result 1-5`)
```


```{r}
N = nrow(results_spt_sentences_long_just_voice_5)
C_I_95 = (1.96 * sd(results_spt_sentences_long_just_voice_5$`result 1-5`)) / sqrt(N)
C_I_95
```









RESULTS: so a small, but not statistically significant, difference in means (more mixture components = higher score) of 6.93 for the arctic voices, but actually a small, but not statistically significant, increase in score of 0.77 for the spt voices.

linear model: 

```{r}
combined_hyp_2_results <- rbind(hyp_2_arctic_results, hyp_2_spt_results)

combined_hyp_2_results <- combined_hyp_2_results %>%
                                       mutate(more_mixture = 
                                                ifelse(voice_num %in% c(1, 4), TRUE, FALSE))

mixture_comp_lm <- lm(result ~ more_mixture, data = combined_hyp_2_results)
summary(mixture_comp_lm)
```
So confirmed by the linear model: a slight reduction in performance (-.077) but not statistically significant. 

```{r}

combined_hyp_2_results <-  combined_hyp_2_results %>%
                                                   mutate(result_1_5 = result/20)

same_domain_lm <- lm(result_1_5 ~ more_mixture, data = combined_hyp_2_results)
summary(same_domain_lm)

```




HYPOTHESIS 3:

SO REDUCED TRAINING SENTENCE EFFECT:

SO:

VOICE 4 VS VOICE 6 ON TEST SENTENCES 1, 3, 4, 5

AND

VOICE 1 VS VOICE 3 ON TEST SENTENCES 6, 7, 8, 9, 10




```{r}

hyp_3_spt_results <- results_spt_sentences_long %>%
                                     filter(voice_num == "4" | voice_num == "6")

hyp_3_spt_t_test <- with(hyp_3_spt_results, t.test(result ~ voice_num, alternative = "greater"))
hyp_3_spt_t_test

```
```{r}
hyp_3_spt_results_6 <-  hyp_3_spt_results %>%
                                                   filter(voice_num == "6") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(hyp_3_spt_results_6$result)         
mean(hyp_3_spt_results_6$`result 1-5`)
sd(hyp_3_spt_results_6$`result 1-5`)
```
```{r}
N = nrow(hyp_3_spt_results_6)
C_I_95 = (1.96 * sd(hyp_3_spt_results_6$`result 1-5`)) / sqrt(N)
C_I_95
```





```{r}

hyp_3_arctic_results <- results_arctic_b_sentences_long %>%
                                     filter(voice_num == "1" | voice_num == "3")

hyp_3_arctic_t_test <- with(hyp_3_arctic_results, t.test(result ~ voice_num, alternative = "greater"))
hyp_3_arctic_t_test

```
```{r}
hyp_3_arctic_results_3 <-  hyp_3_arctic_results %>%
                                                   filter(voice_num == "3") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(hyp_3_arctic_results_3$result)         
mean(hyp_3_arctic_results_3$`result 1-5`)
sd(hyp_3_arctic_results_3$`result 1-5`)
```
```{r}
N = nrow(hyp_3_arctic_results_3)
C_I_95 = (1.96 * sd(hyp_3_arctic_results_3$`result 1-5`)) / sqrt(N)
C_I_95
```




```{r}
combined_hyp_3_results <- rbind(hyp_3_arctic_results, hyp_3_spt_results)

combined_hyp_3_results <- combined_hyp_3_results %>%
                                       mutate(more_training = 
                                                ifelse(voice_num %in% c(1, 4), TRUE, FALSE))

reduced_training_comp_lm <- lm(result ~ more_training, data = combined_hyp_3_results)
summary(reduced_training_comp_lm)
```

so i get a (borderline) significant t-test result for hyp 3 arctic result, but not for the hyp 3 spt result, and no significant effect of more training from the
linear model.

what's going on here?

to do: check that the versions are right for each of the spt sentences (are 4 and 6 where you think they are?):

1 (should be: 4 in position 3 YES, and 6 in position 5 YES) GOOD
3 (should be : 4 in position 1 NO, and 6 in position 8 YES) SO NO GOOD, DISCOUNT VOICE 4 DATA
4 (should be: 4 in position 3 YES, and 6 in position 6 YES) GOOD
5 (should be: 4 in position 1 NO, 6 in position 4 YES) SO NO GOOD, DISCOUNT VOICE 4 DATA


# TO DO: DO THE DF, PLOT AND STATS FOR HYPOTHESIS 4

#S2
```{r}
results_S2_long <- results_cut_down %>%
               select(c(Q5_1:Q5_7)) %>%
               pivot_longer(Q5_1:Q5_7, names_to="version_number", values_to="result")
results_S2_long$result <- as.numeric(results_S2_long$result) 

results_S2_long <-
results_S2_long %>%
                  mutate(voice_num = 
                           ifelse(version_number=="Q5_1", 1,
                           ifelse(version_number=="Q5_2", 2,
                           ifelse(version_number=="Q5_3", 3,
                           ifelse(version_number=="Q5_4", 4,
                           ifelse(version_number=="Q5_5", 5,
                           ifelse(version_number=="Q5_6", 6,
                                  7)))))))

results_S2_long$voice_num <- as.character(results_S2_long$voice_num)
```

```{r}
ggplot(data=results_S2_long, aes(x = voice_num, y = result, na.rm = TRUE)) +
geom_boxplot() +
ggtitle("Sentence 2") +
theme(plot.title = element_text(hjust = 0.45))
```

# TO DO: adapt this
```{r}
results_S2_long <-
results_S2_long %>%
                  mutate(voice_name= 
                           ifelse(voice_num=="1", "Hybrid Voice",
                           ifelse(voice_num=="2", "F0 Voice",
                           ifelse(voice_num=="3", "SPT Original",
                           ifelse(voice_num=="4", "Reference",
                           ifelse(voice_num=="5", "SW Voice",
                           ifelse(voice_num=="6", "ARCTIC A Original",
                           ifelse(voice_num=="7", "PW Voice",
                                  "Reference"))))))))
```


to do: check the sentence order in the survey for sentence 2:

questions for hyp2:

is voice 1 better than voice 2?

```{r}
hyp_4_f0_comparison_results <- results_S2_long %>%
                                     filter(voice_num == "1" | voice_num == "2")

hyp_4_f0_t_test <- with(hyp_4_f0_comparison_results, t.test(result ~ voice_num, alternative = "greater"))
hyp_4_f0_t_test 
```
is voice 1 better than voice 5?

```{r}
hyp_4_sw_comparison_results <- results_S2_long %>%
                                     filter(voice_num == "1" | voice_num == "5")

hyp_4_sw_t_test <- with(hyp_4_sw_comparison_results, t.test(result ~ voice_num, alternative = "greater"))
hyp_4_sw_t_test 
```
is voice 1 better than voice 6?

```{r}
hyp_4_pw_comparison_results <- results_S2_long %>%
                                     filter(voice_num == "1" | voice_num == "7")

hyp_4_pw_t_test <- with(hyp_4_pw_comparison_results, t.test(result ~ voice_num, alternative = "greater"))
hyp_4_pw_t_test 
```
# so no statistically significant results for any of the three: the hypothesis is not supported.

# note that there are clear differences between the three (i.e. 1 is clearly better than the others) but this has not come out in the results. why?


```{r}
hyp_4_results_1 <-  results_S2_long %>%
                                                   filter(voice_num == "1") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(hyp_4_results_1$result)         
mean(hyp_4_results_1$`result 1-5`)
sd(hyp_4_results_1$`result 1-5`)
N = nrow(hyp_4_results_1)
C_I_95 = (1.96 * sd(hyp_4_results_1$`result 1-5`)) / sqrt(N)
C_I_95
```
```{r}
hyp_4_results_2 <-  results_S2_long %>%
                                                   filter(voice_num == "2") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(hyp_4_results_2$result)         
mean(hyp_4_results_2$`result 1-5`)
sd(hyp_4_results_2$`result 1-5`)
N = nrow(hyp_4_results_2)
C_I_95 = (1.96 * sd(hyp_4_results_2$`result 1-5`)) / sqrt(N)
C_I_95
```


```{r}
hyp_4_results_5 <-  results_S2_long %>%
                                                   filter(voice_num == "5") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(hyp_4_results_5$result)         
mean(hyp_4_results_5$`result 1-5`)
sd(hyp_4_results_5$`result 1-5`)
N = nrow(hyp_4_results_5)
C_I_95 = (1.96 * sd(hyp_4_results_5$`result 1-5`)) / sqrt(N)
C_I_95
```



```{r}
hyp_4_results_7 <-  results_S2_long %>%
                                                   filter(voice_num == "7") %>%
                                                   filter(result != "NA") %>%
                                                   mutate("result 1-5" = result/20)
mean(hyp_4_results_7$result)         
mean(hyp_4_results_7$`result 1-5`)
sd(hyp_4_results_7$`result 1-5`)
N = nrow(hyp_4_results_7)
C_I_95 = (1.96 * sd(hyp_4_results_7$`result 1-5`)) / sqrt(N)
C_I_95
```












```{r}
results_real <- results %>%
                 filter(Q4_1 != "")
```

```{r}
age_counts <- table(results_real$Q1)
age_counts
```
```{r}
native_counts <- table(results_real$Q2)
native_counts
```

```{r}
gender_counts <- table(results_real$Q3)
gender_counts
```




